### 2015-07-10 narrative/evaluation.tex
more formatting and fixing.
more wordsmyth and trying to make more sense and uniformity.

Our guiding principles are the basis for the evaluation. These principles are
described in Table~\ref{table:eval}.  We will partition the problem along these
lines and evaluate how the knowledge centric system design we employ can
provide more predictable performance and data quality.

%I dont think this table is right. Knowledge is our independent variable
%and predictability is our dependent variable
\begin{table}[ht]

\centering
\caption{Guiding Principles}
\label{table:eval}
\begin{tabular}{ | p{1.4in} | p{2in} | p{2.5in} | }
  \hline
  {\bf Principle/Metric}                   & {\bf User perspective metric}   & {\bf System perspective metric }\\ \hline
  {\bf Knowledge-centric system}           & More knowledge = faster access to higher quality data &  More knowledge = better resource utilization across the entire hierarchy \\ \hline
  {\bf Predictable Performance Accuracy}   & More predictability = better quality of data &  Accuracy of the time bounds across multiple layers of the storage hierarchy wrote/read in time constrained situations\\ \hline
\end{tabular}
\end{table}

In addition to benchmarking the various SIRIUS methods and tools in isolation,
we will work with our science partners at Princeton University (J. Tromp),
PPPL (C. S. Chang), and U. C. Irvine (Z. Lin), along with the OLCF and SNL,
to evaluate the leading edge applications working with the storage system to
determine performance predictability and data quality.  Our evaluation 
will use the multiple storage layers available on systems at both SNL and the
OLCF.  For example, the sith cluster at the OLCF
(https://www.olcf.ornl.gov/computing-resources/sith/) has its own Lustre
storage system, SSDs on each node, and is connected to the center-wide Lustre
file system. We will perform tests in both the system level (on sith) and in
the user level (on titan), and evaluate our results using our application
knowledge.

>>>>

Our guiding principles are the basis for the evaluation. These principles are
described in Table~\ref{table:eval}, and we will partition the problem along these
lines and evaluate how the knowledge centric system design we employ can
provide more predictable performance and data quality. 
In addition to benchmarking the various SIRIUS methods and tools in isolation,
we will work with our science partners at Princeton University (J. Tromp, C. S. Chang),
and U. C. Irvine (Z. Lin), along with the OLCF and SNL,
to evaluate their applications working with the storage system to
determine performance predictability and data quality.  Our evaluation 
will use the multiple storage layers available on systems at both SNL and the
OLCF, including the sith cluster discussed in the Equipment appendix. 
 We will perform tests in both the system level (on sith) and in
the user level (on titan), and evaluate our results using our application
knowledge.

%I dont think this table is right. Knowledge is our independent variable
%and predictability is our dependent variable
\begin{table}[ht]
\small
\centering
\caption{Guiding Principles}
\label{table:eval}
\begin{tabular}{ | p{1.4in} | p{2in} | p{2.5in} | }
  \hline
  {\bf Principle/Metric}                   & {\bf User perspective metric}   & {\bf System perspective metric }\\ \hline
  {\bf Knowledge-centric system}           & More knowledge = faster access to higher quality data &  More knowledge = better resource utilization across the entire hierarchy \\ \hline
  {\bf Predictable Performance Accuracy}   & More predictability = better quality of data &  Accuracy of the time bounds across multiple layers of the storage hierarchy wrote/read in time constrained situations\\ \hline
\end{tabular}
\vspace{-2ex}
\normalsize
\end{table}

### 2015-07-10 narrative/management.tex
more wordsmyth and trying to make more sense and uniformity.

Careful management will be required to ensure that the problems and delays that are inevitable in any research project
do not unduly disrupt overall progress. To this end, we define a detailed workplan,
establish a  management structure with defined oversight responsibilities, and establish a schedule of regular meetings and
reviews to ensure progress.  We will use google docs to share documents, emails lists for informal communications and a 
weekly phone call in the main research areas to discuss project tasks and milestones.

Dr. Klasky will oversee the outcome of this project,  Dr. Abbasi (ORNL) will lead the Application Interface area, and Dr. Lofstead
will lead the Storage System. This project is focused on the tight integration of application aware-middleware and a storage system backend.
Our team has a strong track record of tight-collaboration, with both Drs. Abbasi and Lofstead working with Dr. Klasky for their Ph.D. at the Georgia
Institute of Technology.  Our structure includes an area lead for each major research area plus
an integration lead responsible for coordinating periodic integration tests. The area leads plus the project PIs
form the management team, which will meet weekly to review progress and revise plans as needed.
We will also have a {\bf Science Advisory Board} consisting of one application scientist, Dr. C. S. Chang (PPPL), and one storage system expert from the 
OLCF, Dr. Vazhkudai (ORNL), who will advise us yearly on our project goals and outcomes and make adjustments accordingly. We will also have our
Math Lead, Dr. Ainsworth, to work with the applied mathematics community to ensure that the hierarchical decomposition of data will work in theory
for current and next generation exascale simulations.

>>>>

Careful management will be required to ensure that the problems and delays that are inevitable in any research project
do not  disrupt overall progress.Here we define a detailed workplan,
establish a  management structure with defined oversight responsibilities, and establish a schedule of regular meetings and
reviews to ensure progress.  We will use google docs to share documents, emails lists for informal communications and a 
weekly phone call in the main research areas to discuss project tasks and milestones.

Dr. Klasky will oversee the outcome of this project,  Dr. Abbasi (ORNL) will lead the Application Interface area, and Dr. Lofstead
will lead the Storage System. This project is focused on the tight integration of application aware-middleware and a storage system backend.
%Our team has a strong track record of tight-collaboration, with both Drs. Abbasi and Lofstead working with Dr. Klasky for their Ph.D. at the Georgia
%Institute of Technology.  
Our structure includes an area lead for each major research area plus
an integration lead responsible for coordinating periodic integration tests. The area leads plus the project PIs
form the management team, which will meet weekly to review progress and revise plans as needed.
We will also have a  yearly meeting with  one application scientist we will partner with,  and one storage system expert from the 
OLCF, who will advise us on our project goals and outcomes and we will make adjustments accordingly. We will also have our
Math Lead, Dr. Ainsworth, to work with the applied mathematics community to ensure that our data-refactoring will work 
for current and next generation exascale math algorithms.

### 2015-07-10 narrative/naming-service.tex
spelling, etc.
more wordsmyth and trying to make more sense and uniformity.

The overriding theme for this proposal of providing a cooperative relationship
between the user and the storage system extends into this area as well.
Negotiating the data quality/retrieval time tradeoff requires additional
metadata.  Providing this functionality requires the naming service be able to
both return a list of data versions and an indication of data quality. This
will be combined with a retrieval time estimate for each version by the
middleware to determine what data version should be retrieved.  This estimate
will be discussed elsewhere in this proposal.

@@

We plan to address scalability problems by continuing with the LWFS and Sirocco
model. LWFS and Sirocco have taken an approach similar to the pure object
stores, but with a focus on the HPC setting. They have abandoned a fully POSIX
compliant metadata service as the default model in favor of a
container/object/fork/address tuple for identifying data similar to those used
for pure object stores. By having a service that addresses the object
collections that comprise a single thing, such as a variable or timestep
output, just enough metadata is maintained to make the storage system usable
without additional heavy lifting by clients.  LWFS demonstrated a POSIX-style
namespace on the side kept in sync using a transaction process like
D2T~\cite{lofstead:2012:txn} showing that this alternative approach can support
traditional POSIX API calls even though the underlying storage system uses a
different model. Because we are not requiring the entire storage space be
addressible from a single tree root, we can offer multiple independent roots
using the Sirocco object storage. We will investigate how to make the naming
and discovery service scalable under the circumstances outlined above.

@@

\begin{tightEnumerate}

\item {\bf Milestone 1}: Demonstrate a metadata service capable of serving both POSIX
clients and our clients, but without consideration for authentication,
authorization, or data migration.

\item {\bf Milestone 2}: Demonstrate a time bounded search approach for finding data
within the storage system to identify data and the current location.  This will
update the cached information in the metadata service to short-circuit future
requests for the data presuming that it does not migrate again soon.

\item {\bf Milestone 3:} Demonstrate incorporating {\color{red}A\&A (what does this stand for CHECK-tsr)} and show scalability under
both application load as well as storage system pressures, showing that we can
tolerate both loads and maintain quality of service.

\end{tightEnumerate}

>>>>

The overriding theme for this proposal of providing a cooperative relationship
between the user and the storage system extends into this area as well.
Negotiating the data quality/retrieval time trade-off requires additional
metadata.  Providing this functionality requires the naming service be able to
both return a list of data versions and an indication of data quality. This
will be combined with a retrieval time estimate for each version by the
middleware to determine what data version should be retrieved.  This estimate
will be discussed elsewhere in this proposal.

@@

We plan to address scalability problems by continuing with the LWFS and Sirocco
model. LWFS and Sirocco have taken an approach similar to the pure object
stores, but with a focus on the HPC setting. They have abandoned a fully POSIX
compliant metadata service as the default model in favor of a
container/object/fork/address tuple for identifying data similar to those used
for pure object stores. By having a service that addresses the object
collections that comprise a single thing, such as a variable or timestep
output, just enough metadata is maintained to make the storage system usable
without additional heavy lifting by clients.  LWFS demonstrated a POSIX-style
namespace on the side kept in sync using a transaction process like
D2T~\cite{lofstead:2012:txn} showing that this alternative approach can support
traditional POSIX API calls even though the underlying storage system uses a
different model. Because we are not requiring the entire storage space be
addressable from a single tree root, we can offer multiple independent roots
using the Sirocco object storage. We will investigate how to make the naming
and discovery service scalable under the circumstances outlined above.

@@

In this project we will first 
%\begin{tightEnumerate}
%
%\item {\bf Milestone 1}: 
demonstrate a metadata service capable of serving both POSIX
clients and our clients, but without consideration for authentication,
authorization, or data migration.
Secondly we will 
%\item {\bf Milestone 2}: D
demonstrate a time bounded search approach for finding data
within the storage system to identify data and the current location.  This will
update the cached information in the metadata service to short-circuit future
requests for the data presuming that it does not migrate again soon.
Finally, we will 
%\item {\bf Milestone 3:} D
demonstrate admission control and show scalability under
both application load as well as storage system pressures, showing that we can
tolerate both loads and maintain quality of service.

%\end{tightEnumerate}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../proposal"
%%% End:
